Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-09-01 paper/paper.tex
\left| \right| and Craigs EPSRC grant number

\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
Research Council [grant number EP/K503058/1]} \and Craig Reilly \\
University of Glasgow, Glasgow, Scotland \\
ruth.hoffmann@glasgow.ac.uk \and \{c.mccreesh.1,c.reilly.2\}@research.gla.ac.uk}

@@

\begin{proof}
Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
implies that $|\nds(p)| -k \leq |\nds(t)|$.

Also, $p \lessmap{k} t$ implies that for each $q \in N(p)\setminus P_k$, where $P_k$
is some subset of $P$ with $|P_k| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
\lesspreceq{k} \nds(t)$.
\end{proof}

@@

\begin{proposition}
    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
\end{proposition}
\begin{proof}
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
\begin{align*}
P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
 = & \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \} \\
 = & \{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} .
\end{align*}
So $\paths(p,q,2) = | \N(p)\cap \N(q)| \leq deg(p)$.

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
|\N(p)\cap \N(q)| - k \leq deg(p) - k \leq deg(t).
\]
As $|\N(p)\cap \N(q)|\leq deg(p) \leq |\N(t)\cap \N(u)|\leq deg(t)$, we have
\[
|\N(p)\cap \N(q)| - k \leq deg(p) - k\leq |\N(t)\cap \N(u)|\leq deg(t)
\]
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2).
\]
\end{proof}

>>>>

\author{Ruth Hoffmann \and Ciaran McCreesh\thanks{This work was supported by the Engineering and Physical Sciences
Research Council [grant number EP/K503058/1]} \and Craig Reilly\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/M506539/1]} \\
University of Glasgow, Glasgow, Scotland \\
ruth.hoffmann@glasgow.ac.uk \and \{c.mccreesh.1,c.reilly.2\}@research.gla.ac.uk}

@@

\begin{proof}
Let $p \lessmap{k} t$.  Then $\deg(p) - k \leq \deg(q)$, by \cref{prop:deg}, which
implies that $|\nds(p)| -k \leq \left| \nds(t) \right| $.

Also, $p \lessmap{k} t$ implies that for each $q \in N(p) \setminus P_k$, where $P_k$
is some subset of $P$ with $\left| P_k \right| \leq k$, $q \lessmap{k} u$, where $u \in N(t)$ and
each $u$ is distinct.  Then $\deg(q) - k \leq \deg(u)$, by \cref{prop:deg}.  Hence $\nds(p)
\lesspreceq{k} \nds(t)$.
\end{proof}

@@

\begin{proposition}
    Let $p,q \in \V(P)$ and $t,u\in \V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
\end{proposition}
\begin{proof}
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
\begin{align*}
P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
 = & \{((p,x),(x,q)) : x\in \N(p) \text{ and } x\in \N(q) \} \\
 = & \{((p,x),(x,q)) : x\in \N(p)\cap \N(q) \} .
\end{align*}
So $\paths(p,q,2) = \left| \N(p)\cap \N(q) \right|  \leq deg(p)$.

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
\left| \N(p)\cap \N(q)\right| - k \leq deg(p) - k \leq deg(t).
\]
As $\left|\N(p)\cap \N(q)\right|\leq deg(p) \leq \left|\N(t)\cap \N(u)\right|\leq deg(t)$, we have
\[
\left|\N(p)\cap \N(q)\right| - k \leq deg(p) - k\leq \left|\N(t)\cap \N(u)\right|\leq deg(t)
\]
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2).
\]
\end{proof}
